% project execution for flowchart project -> I suggest we discuss this first before adding any sections etc.

\subsection{Development Methodology}
\input{../DevelopmentMethodology.tex}

\subsection{Informing the Client}
Our team will have an active, regularly updated, wiki on GitHub and we will also use the GitHub issue tracker with Milestones to keep track of work and goals. We will meet with the client on a weekly or bi-weekly basis to get feedback and discuss progress and problems.

\subsection{Initial Ideas on Solving Some Technical Challenges}
\begin{itemize}
	\item We will use the strategy design pattern to create different classes for the different types of blocks available.
	\item Each block-class will have an execute function that performs the required action.
	\item The flowchart will be implemented as a directed graph with each block holding a reference to its successor(s)
	\item The program will use the Model-View-Controller architectural pattern to separate the interface and the functionality and to simplify flow-chart error checking.
	\item If required, flowcharts will be as stored xml and the program will be able to load these xml files.
\end{itemize}

\subsection{Technologies We will Use}
We plan to use Java with JavaFX to build this application since all our team members know Java and some of us already have experience with JavaFX. It is also platform independent so it can be run on both Windows and Linux.

We will use XML to save flowcharts so a student can save or submit their work. The reason for this choice is that XML is platform independent and can easily be parsed. 

\subsection{What Will The Client Receive}
On completion of the development cycle the client will receive the following:
\begin{itemize}
\item The functional application
\item The program source code
\item Code documentation
\item Requirement and design documentation
\item A user manual for the program.
\end{itemize}